```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("discrim_regularized", "klaR")`

## Tuning Parameters


```{r klaR-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("frac_identity", "frac_common_cov"),
                 default = c("(see below)", "(see below)"))

param <-
  discrim_regularized() %>% 
  set_engine("klaR") %>% 
  tune::tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  dplyr::mutate(
    item = glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameter:

```{r klaR-param-list, echo = FALSE, results = "asis"}
param$item
```

Some special cases for the RDA model: 

* `frac_identity = 0` and `frac_common_cov = 1` is a linear discriminant analysis (LDA) model. 

* `frac_identity = 0` and `frac_common_cov = 0` is a quadratic discriminant analysis (QDA) model. 



## Translation from parsnip to the original package

```{r klaR-cls}
discrim_regularized(frac_identity = numeric(0), frac_common_cov = numeric(0)) %>% 
  set_engine("klaR") %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-zv-conditional.Rmd"}
```

## References

 - Friedman, J (1989). Regularized Discriminant Analysis. _Journal of the American Statistical Association_, 84, 165-175.

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
