```{r, child = "setup.Rmd", include = FALSE}
```

Some special cases for the RDA model: 

* `frac_identity = 0` and `frac_common_cov = 1` is a linear discriminant analysis (LDA) model. 

* `frac_identity = 0` and `frac_common_cov = 0` is a quadratic discriminant analysis (QDA) model. 


# Engine Details

Engines may have pre-set default arguments when executing the model fit call. For this type of model, the template of the fit calls are:

\pkg{klaR}

```{r klaR}
discrim_regularized() %>% 
  set_engine("klaR") %>% 
  translate()
```


The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_discrim_regularized <- function() {
  tibble::tribble(
    ~model,                 ~engine,  ~parsnip,          ~original,  ~default,
    "discrim_regularized",  "klaR",   "frac_common_cov", "lambda",   "varies",
    "discrim_regularized",  "klaR",   "frac_identity",   "gamma",    "varies"
  )
}
convert_args("discrim_regularized")
```

