# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. For this type of model, the template of the fit calls are:

\pkg{earth}

```{r earth}
discrim_flexible() %>% 
  set_engine("earth") %>% 
  translate()
```


The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_discrim_flexible <- function() {
  tibble::tribble(
    ~model,             ~engine, ~parsnip,        ~original,  ~default,
    "discrim_flexible", "earth",  "num_terms",    "nprune",   "all created by forward pass",
    "discrim_flexible", "earth",  "prod_degree",  "degree",   get_arg("earth", "earth.fit", "degree"),
    "discrim_flexible", "earth",  "prune_method", "pmethod",  get_arg("earth", "earth.fit", "pmethod")[2],
  )
}
convert_args("discrim_flexible")
```

