```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("discrim_flexible", "earth")`

## Tuning Parameters

```{r earth-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("num_terms", "prod_degree", "prune_method"),
                 default = c("(see below)", "1L", "'backward'"))

param <-
  discrim_flexible() %>% 
  set_engine("earth") %>% 
  tune::tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  dplyr::mutate(
    item = glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameter:

```{r earth-param-list, echo = FALSE, results = "asis"}
param$item
```

The default value of `num_terms` depends on the number of columns (`p`): `min(200, max(20, 2 * p)) + 1`. Note that `num_terms = 1` is an intercept-only model. 

## Translation from parsnip to the original package

```{r earth-cls}
discrim_flexible(num_terms = integer(0), prod_degree = integer(0), prune_method = character(0)) %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```


## References

 - Hastie, Tibshirani & Buja (1994) Flexible Discriminant Analysis by Optimal 
   Scoring, _Journal of the American Statistical Association_, 89:428, 1255-1270
   
 - Friedman (1991). Multivariate Adaptive Regression Splines. _The Annals of Statistics_, 19(1), 1-67.
