# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. For this type of model, the template of the fit calls are:

\pkg{klaR}

```{r klaR}
naive_Bayes() %>% 
  set_engine("klaR") %>% 
  translate()
```


\pkg{naivebayes}

```{r naivebayes}
naive_Bayes() %>% 
  set_engine("naivebayes") %>% 
  translate()
```

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_naive_Bayes <- function() {
  tibble::tribble(
    ~model,         ~engine,      ~parsnip,     ~original,  ~default,
    "naive_Bayes",  "naivebayes", "smoothness", "adjust",   get_arg("stats", "density.default", "adjust"),
    "naive_Bayes",  "naivebayes", "Laplace",    "laplace",  get_arg("naivebayes", "naive_bayes.default", "laplace"),
    "naive_Bayes",  "klaR",       "smoothness", "adjust",   get_arg("stats", "density.default", "adjust"),
    "naive_Bayes",  "klaR",       "Laplace",    "fL",       get_arg("klaR", "NaiveBayes.default", "fL")
  )
}
convert_args("naive_Bayes")
```

Note that `usekernel` is always set to `TRUE` for the `klaR` engine.
