```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("naive_Bayes", "klaR")`

## Tuning Parameters


```{r klaR-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("smoothness", "Laplace"),
                 default = c("1.0", "0.0"))

param <-
  naive_Bayes() %>% 
  set_engine("klaR") %>% 
  tune::tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  dplyr::mutate(
    item = glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameter:

```{r klaR-param-list, echo = FALSE, results = "asis"}
param$item
```

Note that `usekernel` is always set to `TRUE` for the `klaR` engine.

## Translation from parsnip to the original package

```{r klaR-cls}
naive_Bayes(smoothness = numeric(0), Laplace = numeric(0)) %>% 
  set_engine("klaR") %>% 
  translate()
```

## Preprocessing requirements

The columns for qualitative predictors should always be represented as factors (as opposed to dummy/indicator variables). When the predictors are factors, the underlying code treats them as multinomial data and appropriately computes their conditional distributions. 

```{r child = "template-zv.Rmd"}
```

## References

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
