---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# discrim

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/discrim)](https://cran.r-project.org/package=discrim)
[![Codecov test coverage](https://codecov.io/gh/tidymodels/discrim/branch/main/graph/badge.svg)](https://app.codecov.io/gh/tidymodels/discrim?branch=main)
[![R-CMD-check](https://github.com/tidymodels/discrim/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tidymodels/discrim/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

`discrim` contains simple bindings to enable the `parsnip` package to fit various discriminant analysis models, such as 

-   Linear discriminant analysis (LDA, simple and regularized)
-   Quadratic discriminant analysis (QDA, simple and regularized)
 * Regularized discriminant analysis (RDA, via [Friedman (1989)](https://scholar.google.com/scholar?hl=en&as_sdt=0%2C7&q=%22Regularized+Discriminant+Analysis%22&btnG=))
 * Flexible discriminant analysis (FDA) using MARS features
 * Naive Bayes models
 
## Installation

You can install the released version of discrim from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("discrim")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tidymodels/discrim")
```
  
## Available Engines

The discrim package provides engines for the models in the following table.

```{r, echo=FALSE, message=FALSE}
library(parsnip)

parsnip_models <- get_from_env("models") %>%
  setNames(., .) %>%
  purrr::map_dfr(get_from_env, .id = "model")

library(discrim)

discrim_models <- get_from_env("models") %>%
  setNames(., .) %>%
  purrr::map_dfr(get_from_env, .id = "model")

dplyr::anti_join(
  discrim_models, parsnip_models, 
  by = c("model", "engine", "mode")
) %>%
  knitr::kable()
```

## Example

Here is a simple model using a simulated two-class data set contained in the package:

```{r example}
library(discrim)

parabolic_grid <-
  expand.grid(X1 = seq(-5, 5, length = 100),
              X2 = seq(-5, 5, length = 100))

fda_mod <-
  discrim_flexible(num_terms = 3) %>%
  # increase `num_terms` to find smoother boundaries
  set_engine("earth") %>%
  fit(class ~ ., data = parabolic)

parabolic_grid$fda <-
  predict(fda_mod, parabolic_grid, type = "prob")$.pred_Class1

library(ggplot2)
ggplot(parabolic, aes(x = X1, y = X2)) +
  geom_point(aes(col = class), alpha = .5) +
  geom_contour(data = parabolic_grid, aes(z = fda), col = "black", breaks = .5) +
  theme_bw() +
  theme(legend.position = "top") +
  coord_equal()
```

## Contributing

This project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

- For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question).

- If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/discrim/issues).

- Either way, learn how to create and share a [reprex](https://reprex.tidyverse.org/articles/articles/learn-reprex.html) (a minimal, reproducible example), to clearly communicate about your code.

- Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).
