---
title: "Introduction to discrim"
---

As an example, we'll use a _flexible discriminant analysis_ model of Hastie, Tibshirani, and Buja (1994). This fits a model that uses features generated by the multivariate adaptive regression spline (MARS) model of Friedman (1991). It is able to create class boundaries that are polygons and has built-in feature selection. 

The `parabolic` data from the modeldata package will be used to illustrate:

```{r, message = FALSE}
library(tidymodels)
library(discrim)
tidymodels_prefer()
theme_set(theme_bw())

data(parabolic, package = "modeldata")
```

To create the model, the [discrim_flexible()] function is used along with an engine of `"earth"` (which contains the methods to use the MARS model). We'll set the number of MARS terms to use but this can be tuned via the methods in the tune package.

The `fit()` function estimates the model. `fit_xy()` can be used if one does not wish to use the formula method. 


```{r}
fda_mod <-
  discrim_flexible(num_terms = 3) |>
  # increase `num_terms` to find smoother boundaries
  set_engine("earth") |>
  fit(class ~ ., data = parabolic)
fda_mod
```

Now let's plot the class boundary by predicting on a grid of points then creating a contour plot for the 50% probability cutoff. 

```{r boundary}
#| fig-alt: "Scatter chart. X1 along the x-axis, X2 along the y-axis. points are scattered, with a trend between X1 and X2. Most of the middle points are colored and labeled Class2, with the remaining points labeled Class1. Two connected straight lines, doing its best to separate the two classes."
parabolic_grid <-
  expand.grid(X1 = seq(-5, 5, length = 100),
              X2 = seq(-5, 5, length = 100))

parabolic_grid <- 
  parabolic_grid |> 
  bind_cols(
    predict(fda_mod, parabolic_grid, type = "prob")
  )

ggplot(parabolic, aes(x = X1, y = X2)) +
  geom_point(aes(col = class), alpha = .5) +
  geom_contour(data = parabolic_grid, aes(z = .pred_Class1), col = "black", breaks = .5) +
  coord_equal()
```
